ShrinkNets: Learning Network Size while Training

### 2018-02-10 paper/ICML/introduction.tex
edit intro

\noindent\textbf{2.} We implement our technique so as to remove entire neurons,
therefore leading not only to small and well-performing networks, but also
dense, which means higher inference performance. Furthermore, our switching
layers used during training can be savely removed before the model is used for
inference, leading to zero additional overhead.

@@

\noindent\textbf{4.} We evaluate ShrinkNets with both fully-connected as well as
convolutional neural networks. For \texttt{CIFAR10}, we achieve the same
accuracy than a traditionally trained network while reducing the network size by
a factor of $2.2x$. Further, when willing to sacrifice only $1$\% of
performance, ShrinkNets finds networks which are 35\% smaller. All in all, this
leads to speedups in inference time of up to 6x.

>>>>

\noindent\textbf{2.} We extend our technique to remove entire neurons,
 leading not only to smaller networks, but also
dense matrices, which yield improved inference times as networks shrink. Furthermore, our switching
layers used during training can be safely removed before the model is used for
inference, meaning they add no additional overhead at inference time.

@@

\noindent\textbf{4.} We evaluate ShrinkNets with both fully-connected as well as
convolutional neural networks. For \texttt{CIFAR10}, we achieve the same
accuracy as a traditionally trained network while reducing the network size by
a factor of $2.2X$. Further, while sacrificing just $1$\% of
performance, ShrinkNets finds networks that are 35X smaller. All in all, this
leads to speedups in inference time of up to 6X.
